%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
\usepackage{inconsolata}
\usepackage{XCharter}
\setmonofont{Inconsolata}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[inline]{enumitem}
\usepackage{hyperref}
\urlstyle{same}
\usepackage{fancyhdr}
\usepackage{lastpage}

\hypersetup{pdfauthor={Simon Bihel},
            pdftitle={Simon Bihel - R\'esum\'e}}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
% \fancyfoot[C]{\thepage{}~of~\pageref{LastPage}}
\fancyfoot[R]{\hfill\tiny{\emph{Last updated on \today}}\hspace*{-1in}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{%
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{}\vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\basicItem}[2]{%
  \item\small{%
    \textbf{#1}{\ifx&#2&\else\ifx&#1&\else: \fi#2\vspace{-2pt}\fi}
  }
}

\newcommand{\headingItem}[4]{%
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\headingSubItem}[2]{\basicItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}


% \usepackage{showframe}
\begin{document}

% -----------------------------------------------------------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Simon Bihel} & \href{mailto:simon@simonbihel.me}{\texttt{simon@simonbihel.me}}\\
  \href{https://simonbihel.me}{\texttt{simonbihel.me}} & +44 7484 121815 \\
\end{tabular*}


% -----------------------------------------------------------------------------
\section{Education}
\begin{itemize}[leftmargin=*]
  \headingItem{University of Rennes 1 \& ENS Rennes}{Rennes, France}%
    {MSc in Computer Science, research track}{2016--2018}
  \headingItem{University of Rennes 1 \& ENS Rennes}{Rennes, France}%
    {BSc in Computer Science, research track}{2013--2016}
\end{itemize}


% -----------------------------------------------------------------------------
\section{Experience}
\begin{itemize}[leftmargin=*]
  \headingItem{Nexmo}{London, United-Kingdom}{Software Developer in Test}{November 2018--Present}
    \begin{itemize}
      \basicItem{Voice API}{member of the Real-Time Communication stack.}
      \basicItem{}{Testing: maintenance of the test suite (e.g.\ abstraction and generation of tests, parallelisation).}
      \basicItem{}{Monitoring: facilitate incident impact measurement, track API usage, alerting (pushed for on-call).}
      \basicItem{}{Investigations: understanding test failures or abnormal behaviours across the services.}
      \basicItem{}{Development: built a rating (billing) engine with a small team, various internal changes in services.}
      \basicItem{}{DevOps: AWS migration, maintenance of on-demand test environments (e.g.\ dockerise services, debugging).}
    \end{itemize}\vspace{-5pt}

  \headingItem{KTH}{Stockholm, Sweden}{Research Intern}{February 2018--June 2018}
    \begin{itemize}
      \basicItem{Adaptation of Amplified Unit Tests for Human Comprehension}{Generating natural language explanations for Java unit tests generated by DSpot.}
    \end{itemize}\vspace{-5pt}

  \headingItem{KAIST}{Daejeon, South-Korea}{Research Intern}{March 2017--August 2017}
    \begin{itemize}
      \basicItem{Automated Test Data Generation for Dynamically Typed Programming Languages}{Survey on Test Data Generation from scratch for dynamic languages such as Python.}
    \end{itemize}\vspace{-5pt}

  \headingItem{IRISA \& INRIA}{Rennes, France}{Research Intern}{May 2016--July 2016}
    \begin{itemize}
      \basicItem{Specifying the Experimental Scenarios for Simulated Cloud Studies}{Designing an API for SimGrid, a distributed systems simulator, targeting researchers' needs for cloud simulations.}
    \end{itemize}\vspace{-5pt}
\end{itemize}


% -----------------------------------------------------------------------------
\section{Skills}
\begin{itemize}[leftmargin=*]
  \headingSubItem{Languages}{Go, Python, Rust}
  \headingSubItem{Libraries}{AST manipulations}
  \headingSubItem{Testing}{Pytest, \_Unit, Mutation Testing}
  \headingSubItem{Automation}{Docker, Puppet, Terraform, Nomad}
  \headingSubItem{Continuous Integration}{Jenkins, Travis, SonarCloud}
  \headingSubItem{Monitoring}{Grafana, Prometheus, ELK Stack}
\end{itemize}


% % -----------------------------------------------------------------------------
% \section{Languages}
% \begin{itemize}[leftmargin=*]
%   \headingSubItem{French}{Mother tongue}
%   \headingSubItem{English}{Fluent}
% \end{itemize}


\end{document}
